---
author: Vivian Vy Le
date: '`r format(Sys.Date())`'
title: Penguins
subtitle: Week 6 Lab Assignment
output:
  html_document:
    toc: true
    theme: spacelab
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,  fig.path = "../Output/")
```

# Introduction
In BIOL 551 lecture, we learned how to edit images and create tables with Rmarkdown. This is the assignment for Week 6 Thursday Lab. For this assignment, I used palmerpegnuins dataset to create a plot and a table.

## Load library
The dataset used for this document is palmerpenguins.
```{r}
library(tidyverse)
library(palmerpenguins)
library(here)
library(kableExtra)
```

## Load data
```{r}
glimpse(penguins)
view(penguins)
```

### Data analysis
The original data measured the penguins in grams. Here, the analysis converted the measurement from grams to kilograms.

```{r}
weight_data <-penguins %>%
  mutate(body_mass_kg = body_mass_g/1000) %>%
  drop_na() %>%
  relocate(body_mass_kg, .after=body_mass_g) %>% #move the column next to body mass grams
  rename("Species" = species,
         "Sex" = sex,
         "Islands" = island) #renaming the columns so that they are capitalized 
view(weight_data)
```


#### Plotting data
After analyzing the data, I plotted the body mass across the penguins species and island. I wanted to compare the differences between sexes. species, and islands.

```{r, penguin_weight, out.width = "50%", fig.align='center'}
weight_data %>%
  ggplot(aes(x = Sex, y = body_mass_kg, color = Sex)) +
  geom_point() + #show all of the data points 
  geom_boxplot() + #showing five-number summary for data
  facet_wrap(~Islands) +
  labs(title = "Comparing Penguin Body Weight Across Islands",
       caption = "Data used from palmerpenguins",
       x = "Sex",
       y = "Body Mass (kg)",
       color = "Sex") +
  theme(plot.title = element_text(hjust = 0.5), #centers the title
        axis.text = element_text(size = 10), #changes the text size of the axes
        panel.border = element_rect(fill = NA, color = "black")) + #adds a black border to the plot
  scale_color_viridis_d() #using viridis for the outline of the boxplot
```


#### Data table
I created the table and grouped the information based on island, species, and sex.

The data table has averages for:

 -  body mass
 - flipper length
 - bill length
 - bill depth  

```{r, penguin_table, fig.align='center'}
weight_data %>%
  group_by(Islands, Species, Sex) %>% #group the data by island, species, and sex for the table
  summarise("Avg Body Mass (kg)" = mean(body_mass_kg),
            "Avg Flipper Length (mm)" = mean(flipper_length_mm),
            "Avg Bill Length (mm)" = mean(bill_length_mm),
            "Avg Bill Depth (mm)" = mean(bill_depth_mm)) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kbl(caption = "Comparing Average Measurements Across Penguin Species and Islands") %>%
  kable_minimal() %>%
  pack_rows("Biscoe", 1,4) %>% #groups the rows to the island name, groups rows 1-4
  pack_rows("Dream", 5,8) %>% #groups rows 5-8
  pack_rows("Torgersen", 9,10) #groups rows 9-10
```