---
title: "Week 8 Homework"
author: "Vivian Vy Le"
date: '2022-03-17'
output: 
  html_document:
    toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,  fig.path = "../Output/")
```

# Introduction
In BIOL 551, we learned how to create functions. For this assignment, I created a few functions for my data analysis and plot using the PalmerPenguin data set. 

## Load Libraries
```{r}
library(tidyverse)
library(here)
library(palettetown)
library(palmerpenguins)
```

### View Libraries 
```{r}
glimpse(penguins)
view(penguins)
```

## Data analysis

Here, I am creating a function to calcuate for the ratio of the bill length and depth. I also created a function to convert grams to kilograms.
```{r}
bill_ratio<-(penguins$bill_depth_mm/penguins$bill_length_mm) #function to calculate the ratio of bill depth and flipper length

billratio <-function(penguins){
  bill_ratio<-(penguins$bill_depth_mm/penguins$bill_length_mm)
  return(bill_ratio)
}

body_mass_kg <-(penguins$body_mass_g)/1000 #function to convert grams to kilograms

```


## Plotting data

With the functions I made in the previous chunk, I then created a plot. The first function I used was to create a function for the color palette. I chose to use the pokemon Roselia as a color palette generator and picked the first 4 colors. I created a function for my first plot. I added the titles and captions after my plot function.

```{r, mass_vs_bill_ratio, outwidth = "60%", fig.align='center'}
pal <- "Roselia" %>% ichooseyou(4)

plot1 <- function(data, x, y){
ggplot(penguins,
       aes(x = {{x}}, 
           y = {{y}}, color = species, fill = species)) +
  geom_point() + #showing all the data points
  geom_smooth(method = "lm") + #used a linear model for graphing
  scale_color_manual(values = pal) +
  scale_fill_manual(values = pal) +
  facet_wrap(~sex) #wanted to see the differences between sex
}

plot1(penguins, x = body_mass_kg, y = bill_ratio) +
  labs(title = "Comparing Body Mass and Bill Depth and Length Ratio", #adding titles for plot and axis
       x = "Body Mass (kg)",
       y = "Bill Depth and Length Ratio (mm)",
       color = "Species",
       fill = "Species",
       caption = "Source: PalmerPenguins")
```
To make sure my functions work, I plotted different data. I chose a different pokemon, Illumise, for the color palette. Then, I plotted flipper length to compare to body mass in kilograms.

```{r, mass_vs_flipper, outwidth = "60%", fig.align='center'}
pal <- "Illumise" %>% ichooseyou(4) #used a different pokemon color palette to show differnces between plots

plot1(penguins, x= body_mass_kg, y = flipper_length_mm) + #changed the y data to be flipper length
  labs(title = "Comparing Body Mass and Flipper Length Ratio", #changed the titles to reflect changes in the graphed data.
       x = "Body Mass (kg)",
       y = "Flipper Length (mm)",
       color = "Species",
       fill = "Species",
       caption = "Source: PalmerPenguins")
```

