---
title: "Week_7_Good_vs_Bad_Plot"
author: "Vivian Vy Le"
date: '2022-03-15'
output: 
  html_document:
    toc: TRUE
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,  fig.path = "../Output/")
```

# Introduction
In BIOL 551 lecture, we read and learned how to make good and bad plots. We were challenged to create good and bad plots to the best of our abilities. I decided to use a previous TidyTuesday data from 2020, **Broadway Weekly Grosses**.

## Load Library
```{r}
library(tidyverse)
library(here)
library(ggplot2)
library(palettetown)
library(lubridate)
library(ggpubr)
library(jpeg)
library(ggfortify)
```

### Load Data
The data used for this assignment comes from TidyTuesday 2020: **Broadway Weekly Grosses**
```{r}
grosses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-28/grosses.csv', guess_max = 40000)
```
### View Data
```{r}
glimpse(grosses)
view(grosses)
```

## Musicals from Debuting 2000 until 2016
The data was recorded from June 1985 to March 2020. In order to narrow this data set, I focused on a few musicals that debuted in 2000 to 2016. Some of these musicals are still showing while some have closed the curtains. The musicals included in the analysis are, Hamilton, Wicked, The Lion King, Mamma Mia!, and Waitress.

### Data Analysis
```{r}
#filtering out a few shows from the original data
grosses_2000 <- grosses %>%
  filter(show %in% c("Hamilton", "Wicked", "The Lion King", "Mamma Mia!", "Waitress")) %>%
  mutate(year = year(week_ending), #separated year and month
         month = month(week_ending)) %>%
  select(month, year, show, weekly_gross_overall, weekly_gross, potential_gross, avg_ticket_price) %>%
  group_by(month, year, show) #groups the data by show and time
view(grosses_2000)

#using the original data for the time, makes the plot have a continuous x value for good plot
ham_week <- grosses %>% 
  filter(show == "Hamilton") %>%  #filtering out Hamilton
  select(show, week_ending, weekly_gross, potential_gross)  #selecting a few columns 
view(ham_week)

```

### Plotting a Bad Plot
This is an example of a bad plot. There are a few reasons why this is considered a bad plot:

  - The titles of the plot and axes are not informative.
  - There are a lot of data plotted, however the plot does not reflect all of the shows represented in the data.
  - The axis titles do not have a form of measurement.
  - The text on the plot are in informal English.
  - One of the colors used is a neon color, which makes it difficult to read the graph.
  
  
```{r, badplot, outwidth = "50%", fig.align='center'}
broadway <- here("Week_7", "Data", "broadway2020.jpg") #creating an object with an image from computer
broadway <- jpeg::readJPEG(broadway) #function to make R read a jpeg
grosses_2000 %>%
  ggplot(aes(x = year), color = show) + #setting color for the shows
  background_image(broadway) + #add the picture as the background for the graph
  geom_line(aes(y=weekly_gross_overall, col = show)) +
  scale_y_continuous(labels = scales::comma) +
  labs(title = "here we go again!", #mammia mia! reference
       subtitle = "let's have a celebration the glinda way", #wicked reference
       x = "i live another 50 years, it's not enough", #hamilton reference
       y = "money, money, money", #mammia mia! reference
       color = "She's imperfect but she tries", #waitress reference
       caption = "source: probs playbill idk") +
  scale_color_manual(values = pokepal(167)) +
  theme_minimal()
```

### Plotting a Good Plot
This is an example of a bad plot. There are a few reasons why this is considered a good plot:

  - The titles on the plot and axes are informative and are written in formal English.
  - Instead of having all weekly gross data for all of the shows, this plot focuses on one show.
  - The colors used are visible and are easy to read. They also are contrasting colors to each other, so both filled areas are visible.
  - This plot is using a stacked area chart. With this we can see the weekly gross changes over time. It is useful for this type of data since we are looking at when Hamilton opened in 2015 until 2020.
  
```{r, goodplot, outwidth = "50%", fig.align='center'}
ggplot(data = ham_week, mapping = aes(x=week_ending)) +
  geom_area(aes(y = weekly_gross, fill = "Weekly Gross")) + #creating a filled area for weekly gross
  geom_area(aes(y = potential_gross, fill = "Potential Gross")) + #creating a filled area for potential gross to compare weekly gross
  labs(title = "Weekly Ticket Sales For Hamilton: An American Musical", #adding titles and subtitles for plot
       subtitle = "Gross from 2015 until 2020",
       x = "Time",
       y = "Gross in Dollars",
       caption = "Source: The Broadway League/TidyTuesday 2020",
       fill = "Type of Gross") +
  scale_fill_manual(values = pokepal(13)) + #adding colors to match the parchment outfits in the musical, using weedle as a color palette
  theme(panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5), #centering the text
        plot.subtitle = element_text(0.5),
        axis.text = element_text(size = 10)) +
  theme_minimal()
```

