---
title: "Week 13 HW"
author: "Vivian Vy Le"
date: '2022-04-28'
output: 
  html_document:
    toc: TRUE
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Introduction

In class, we learned how to create loops and map functions. For this assignment, we will create loop and map functions to calculate the mean and standard deviation for temperature and light intensity data collected in tide pools in Oregon.

##Load Library
```{r}
library(tidyverse)
library(here)
```

## Load Data

There are 4 files to create a loop with. First, I have to set up the file path.
```{r}
path_hw<- here("Week_13", "Data", "homework") #creating a file path

files_hw <- dir(path = path_hw, pattern = ".csv") #selecting for specific files

data_hw <- data.frame(matrix(nrow = length(files_hw), ncol = 5)) #making an empty dataframe with one row for each file and 5 columns

colnames(data_hw) <- c("filename", "mean_temp", "stdev_temp", "mean_light" , "stdev_light") #creating column names for dataframe

data_hw
```
## Data Analysis

### Creating a loop

Next, I will fill in the table with the average and standard deviation for temperature and light intensity from the files. I need to create a loop for this.


```{r}
for(i in 1:length(files_hw)){
  data_loop<-read_csv(paste0(path_hw, "/", files_hw[i]))
  data_hw$filename[i] <-files_hw[i]
  data_hw$mean_temp[i] <-mean(data_loop$Temp.C, na.rm = TRUE) #calculating mean for temp
  data_hw$stdev_temp[i] <-sd(data_loop$Temp.C, na.rm = TRUE) #calculating stand dev for temp
  data_hw$mean_light[i] <- mean(data_loop$Intensity.lux, na.rm = TRUE) #calculating mean for intensity
  data_hw$stdev_light[i] <- sd(data_loop$Intensity.lux, na.rm = TRUE) #calculating stand dev for intensity
}
data_hw
```

### Using purr

Here, I am using the purr package instead of a **for loop**.

```{r}
files_purr <- dir(path = path_hw, pattern = ".csv", full.names = TRUE) #bringing files with purr
files_purr #can see the entire path name for files

data_purr <- files_purr %>%
  set_names() %>%
  map_df(read_csv, .id = "filename") %>%
  group_by(filename) %>%
  summarise(mean_temp = mean(Temp.C, na.rm = TRUE), #calculating mean for temp from the files
            sd_temp = sd(Temp.C, na.rm = TRUE), #calculating stand dev for temp from files
            mean_light = mean(Intensity.lux, na.rm = TRUE), #calculating mean for intensity
            sd_light = sd(Intensity.lux, na.rm = TRUE)) #calculating stand dev for intensity
data_purr
```

