---
title: "Week 12 HW"
author: "Vivian Vy Le"
date: '2022-04-21'
output: 
  html_document:
    toc: TRUE
    theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.path = "../Output/")
```

# Introduction
After learning about stringr and working with factors and metacharacters, the assignment for Week 12 is to clean up the intertidal datasets.

## Load library
```{r}
library(tidyverse)
library(here)
library(LaCroixColoR)
library(janitor)
library(ggplot2)
```

## Load Data
```{r}
intertidialdata <-read_csv(here("Week_12", "Data","intertidaldata.csv"))
lat_data <-read_csv(here("Week_12", "Data", "intertidaldata_latitude.csv"))
```
### View Data
```{r}
view(intertidialdata)
view(lat_data)
```

## Cleaning up the data

Before analyzing and plotting the data, I am cleaning up the data. Here, I am making sure the columns are either fully characters or variables.

```{r}
intertidal_clean <- intertidialdata %>%
  clean_names() #reformat the column titles

intertidal_work <- intertidal_clean %>%
  mutate_at("quadrat", str_replace, "\\,", " ") %>% #removes any commas in the column
  mutate_at("quadrat", str_replace, "\\.", " ") %>% #removes any periods in the column
  mutate_at("quadrat", str_replace, "[0-9]", " ") %>% #removes any numbers in the column
  rename("whelks" = whelks_counts) %>% #rename the columns to remove the word counts
  rename("crabs" = crabs_counts) %>%
  rename("stars" = stars_counts)
view(intertidal_work)
write.csv(intertidal_work, "intertidaldata_clean.csv")
```


## Data analysis

I am organizing the data so that I can get the counts for the barnacles at each tide height. I am also making sure that the tide heights are considered as factors.

```{r}
values <- intertidal_work %>%
  group_by(site, quadrat) %>%
  relocate(quadrat, .after = site) %>% 
  pivot_longer(small_barnacles:gooseneck_barnacles, #getting counts of barnacles at each quadrat site
               names_to = "variables",
               values_to = "counts") %>%
  mutate(quadrat = factor(quadrat, 
                          levels = c("Low", "Mid", "High"))) #turning the quadrat into factors
```

## Plotting data

After organizing and cleaning the data, the plot will show the counts of the various barnacles at each tide height.

```{r, barnacle_plot, outwidth = "60%", fig.align='center'}
values %>%
  ggplot(aes(x = quadrat, y = counts, fill = variables)) +
  geom_bar(position = "dodge", #creates a grouped bar graph instead of stacked
           stat = "identity") +
  labs(title = "Barnacle Coverage Within Tide Levels",
       x = "Quadrat",
       y = "Count",
       fill = "Variables") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title = element_text(face = "bold"), #axis text changed to bold
        axis.text = element_text(size = 10)) + #changed axis text size
  scale_fill_manual(values = lacroix_palette("Pamplemousse", n = 3, type = "continuous"))
```

